Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow

### 2012-02-18 Text/introduction.tex
Started editing the text. More stuff in the introduction.

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient depending on the
capillary number $Ca$ regime. For example, for $Ca<0.7$ the flow has a vortex in front of the
bubble, but for the larger capillary number it hasn't. In case of mass
sources to be comparable of the representative unit cell (inhomogenous
situation), one cannot estimate  the strategies to measure the volumetric mass transfer coefficient
are presented. The strategies of how to speed up simulations, what the boundaries conditions are
thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
domain concentration is taken as the characteristic concentration. Though more difficult to setup
simulations with a few unit cells can give additional information about how well the liquid slug is
mixed. The work is of use to people performing mass transfer numerical simulations within the
lattice Boltzmann context.
\end{abstract}

\section{Introduction}
The volumetric mass transfer coefficient is a very important characteristic for microchannels 
design \cite{kreutzer-overview}. It allows to
properly manufacture a microchannel with necessary properties to ensure that chemical
reactions are performed in the best manner. Many chemical microchannel configurations
\cite{kreutzer-pressure-drop}  The flow for microchannels we focus on is the bubble train
motion, where bubbles organized in a train are traveling through the liquid media. This
configuration is interesting due to several reasons: hydrodynamic velocity patterns are completely
different for different capillary numbers, the bubble occupies the significant part of the unit cell
and the flow can be assumed periodic.

>>>>

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient addressing the
following challenges: the flow pattern  depends on the capillary number $Ca$ regime, i.e. for
$Ca<0.7$ the flow has a vortex in front of the
bubble, but for the larger capillary number it hasn't;  the mass sources is comparable of the
representative unit cell size (inhomogenous situation is different from the homogenous well-mixed
media \cite{jos-mass}); the connection between time and space domains for moving bubbles; the
definition of the mass transfer coefficient which is defined through the characteristic
concentration (inlet/outlet concentration, average concentration). The following boundary conditions
were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
simulations. It was shown that the time dependent average concentration to be a characteristic
concentration produce robust results, though a bit overpredicted. The inlet/outlet flux averaged
concentration to be a characteristic concentration produce unreliable results. In comparison, a few
unit cells open boundaries conditions resemble physical situation most and are harder to conduct
but provide the volumetric mass transfer coefficient based only on the spatial information for the
capillary number $Ca>0.7$. As well, a few unit cells simulations can provide more information about
mixing in the liquid slug in comparision with the periodic boundary conditions. We show
that all presented in literature strategies are extreme limits of one equation,
Eq. {\color{red} give equation number here}. Finally, the correlation for different Peclet numbers
is compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
comparison. The work is of use to people performing mass transfer numerical simulations for bubble
train flow in microchannels and within the
lattice Boltzmann context.
\end{abstract}

\section{Introduction}
The monolith reactors during last years are getting more attention as alternative to slurry
reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. The bubble flow we focus in
this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
a liquid medium of equal sized, long in comparison with the height bubbles in microchannels, see
Fig. \ref{fig:benchmark:hydro}. This flow regime
is usually characterized by surface tension dominance over inertia and viscous effects and by
comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
in macroscopic counterparts: such as thin films \cite{bretherton} which can remarkably enhance mass
transfer in the film from gas or wall; the plug flow nature that separates liquid slugs from each
other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
of Bretherton-Taylor bubble train flow: continous flow analyzers, lung openings, chemical reactions
as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
lot of different application references in extensive reviews \cite{kreutzer-overview,
gupta-review,yue-mass}.

Among different applications of microchannel flows, this work is focused on the mass transfer
study from gas to liquid. The good understanding of mass transfer and how it depends on the
parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
manufacture a microchannel with necessary properties to ensure that chemical
reactions are performed in the best manner \cite{bercic}. A number 
  This
configuration is interesting due to several reasons: hydrodynamic velocity patterns are completely
different for different capillary numbers, the bubble occupies the significant part of the unit cell
and the flow can be assumed periodic.
